Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-13 paperIEEE.tex
smal fix.
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@127 db7c848b-7755-4df2-b763-8796797afa52

The data distribution benchmarks have been performed on a cluster using dual
processor Intel Xeon X5690 CPUs (3.47\,GHz), 24\,GB main memory per node,
10\,GBit/s Ethernet and QDR Infiniband. Intel ICC 2017 has been used with CMake
3.2 release mode settings to compile the software stack. To benchmark the data
distribution we used two datasets: The David statue at 2\,mm resolution (as in
\fig{fBenchmarks (middle)}, but in 2\,mm resolution) and 3D volumes of spike
frequencies of an electrical simulation of three million neurons
(\fig{fBenchmarks} (right)).

>>>>

The data distribution benchmarks have been performed on a cluster using dual
processor Intel Xeon X5690 CPUs (3.47\,GHz), 24\,GB main memory per node,
10\,GBit/s Ethernet and QDR Infiniband. Intel ICC 2017 has been used with CMake
3.2 release mode settings to compile the software stack. To benchmark the data
distribution we used two datasets: The David statue at 2\,mm resolution (as in
\fig{fBenchmarks} (middle), but in 2\,mm resolution) and 3D volumes of spike
frequencies of an electrical simulation of three million neurons
(\fig{fBenchmarks} (right)).
